### 2016-02-03 inputs/introduction.tex

a wide range of genetic analyses: in fact, most models and software for 

@@

studies (GWAS) can not handle missing data and require complete datasets (e.g. \cite{hayes2009invited}). 
SNP-chips represent one of the leading genotyping technologies, and produce 
datasets that, after markers and individuals with low call-rate are edited out, 

@@

is due to both intrinsic properties of the technology - e.g., low coverage - 

@@

yield very high imputation accuracy: for instance, $>$95\% correctly imputed 

@@

Such methods can be applied to GBS data, too (see for instance 
\cite{huang_efficient_2014} and \cite{swarts_novel_2014} 
for applications in rice and maize). When a reference 

@@

are therefore ordered. However, GBS data may be generated 

@@

alignment is not possible and SNPs are therefore unordered. Unordered 

@@

exploitation of linkage disequilibrium (LD) and haplotype reconstruction 

@@

Compared to SNP-chip data, GBS data are more challenging: many more 

@@

important crop species: the forage crop alfalfa (\emph{Medicago sativa}), for 
which a reference genome is not available yet, and the 
cereal crop rice (\emph{Oryza sativa}) whose reference genome has been 
assembled in 2005 \cite{international_rice_genome_sequencing_project_map-based_2005}, and
was recently updated \cite{kawahara_improvement_2013}. We compared the imputation 
efficiency of four general data-imputation methods (Mean Value Imputation, 
K-Nearest Neighbour Imputation, Singular Value Decomposition Imputation 
and Random Forest Imputation) with the performance of two methods specific 

@@

implemented in the software package Beagle, %and haplotype reconstruction around the recombination site
and the FILLIN algorithm implemented in the programming suite Tassel). The relative efficiency of 
the different imputation methods was assessed in terms of  
accuracy and computation time. Accuracy was measured in terms
of gross fraction of correctly imputed genotypes, and within
genotype classes (major/minor homozites and heterozigotes, when present).

>>>>

a wide range of genetic analyses. In fact most models and software for 

@@

studies (GWAS) can not handle missing data and require complete datasets (e.g. \cite{hayes2009invited,aulchenko2007genabel,endelman2011rrblup,perez2014genome}). 
SNP-array represent one of the leading genotyping technologies and produce 
datasets that, after low call-rate filtering, 

@@

is due to both intrinsic properties of the technology

@@

yield very high imputation accuracy. For instance, $>$95\% correctly imputed 

@@

The same imputation methods can also be applied to GBS data (see \cite{huang_efficient_2014} and \cite{swarts_novel_2014} for applications in rice and maize). When a reference 

@@

are therefore ordered, thus allowing the exploitation of local linkage disequilibrium (LD).
However, GBS data may be generated 

@@

alignment is not possible and SNPs are therefore considered unordered. Unordered 

@@

exploitation of linkage disequilibrium and haplotype reconstruction 

@@

Compared to SNP-array data, GBS is more challenging: many more 

@@

important crop species:
the cereal crop rice (\emph{Oryza sativa L.}) whose reference genome has been 
assembled in 2005 \cite{international_rice_genome_sequencing_project_map-based_2005}, and updated in 2013 \cite{kawahara_improvement_2013},
and
the forage crop alfalfa (\emph{Medicago sativa L.}), for 
which a reference genome is not available yet. When necessary, alfalfa genotypes
were mapped on the close relative \emph{Medicago truncatula L.}, a model species
for legumes, whose genome is available \cite{young_medicago_2011}.
The species were chosen 
as representative of very different scenarios, alfalfa being autotetraploid
with high heterozygosity and rice being diploid with essentially 100\% homozygozity.
The presented study thus encompasses a wide span of real application cases.\\
We compared the imputation efficiency of four general imputation methods (Mean
Value Imputation, K-Nearest Neighbour Imputation, Singular Value Decomposition
Imputation and Random Forest Imputation) with the performance of two methods specific 

@@

implemented in the software package Beagle, \textcolor{red}{and haplotype
reconstruction around the recombination site}, implemented in the FILLIN algorithm
as part of Tassel suite). The four general algorithms were chosen as well known imputation strategies implemented in several freely available software libraries and frameworks. The two genotype-specific methods represent the state of the art for genotypes lacking pedigree information.\\
The relative efficiency of the different imputation methods was assessed in terms of 
accuracy and computation time. Accuracy was measured as fraction of 
correctly imputed genotypes, and within genotype classes 
(major/minor homozigotes, and heterozigotes, when present).
